A Tutorial on Tailored Power Simulations for Experimental Study Designs with Generalized Linear Mixed Models

### 2023-09-15 docs/appendix.Rmd

>>>>

# Appendix:

**Note**: At the moment, this file contains only a few fragments of code but is not mentioned in the manuscript. Some of these pieces might be used in a later stage of the probject (e.g. after the first round of peer review).

## A different model equation with random slopes

$$
logit(P_{si}) = (\beta_0 + u_{0p} + u_{0i})  + \beta_e \cdot expert_p + \beta_a \cdot advice\_present_{si} + (\beta_c + u_{1p}) \cdot advice\_correct_{si} + \beta_{ea} \cdot expert_{p} \cdot advice\_present_{si} 
$$
